Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration

### 2025-02-11 doc/protocol.qmd

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    orcid: "0000-0002-7038-4770"
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    orcid: "0000-0003-4169-2616"
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
    url: "https://www.stenoaarhus.dk/"
  - id: au
    name: Aarhus University
    country: Denmark
    url: "https://www.au.dk/"
  - id: ku
    name: Copenhagen University
    country: Denmark
    url: "https://www.ku.dk/"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
format:
  html: default
  typst:
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: typst
    text: PDF
    icon: file-pdf
---
